### 2008-12-20 talk/ecoop2009/intro.tex
kill a picture, as it was only loosely referenced by the text

\begin{figure}[h]
\begin{center}
\includegraphics[width=.6\textwidth]{diagram0}
\caption{PyPy infrastracture for generating an interpreter of a
  language $L$ for several platforms}\label{pypy-fig}
\end{center}
\end{figure}

@@

Despite having been specifically developed for Python, the PyPy infrastructure
can in fact be used for implementing other languages. Indeed, there were
successful experiments of using PyPy to implement several other languages such
as Smalltalk \cite{BolzEtAl08}, JavaScript, Scheme and Prolog.
As suggested by Figure~\ref{pypy-fig}, a portable interpreter for a
generic language $L$  can be
easily developed once an interpreter for $L$ has been implemented in
RPython.

>>>>

\commentout{
\begin{figure}[h]
\begin{center}
\includegraphics[width=.6\textwidth]{diagram0}
\caption{PyPy infrastracture for generating an interpreter of a
  language $L$ for several platforms}\label{pypy-fig}
\end{center}
\end{figure}
}

@@

Despite having been specifically developed for Python, the PyPy infrastructure
can in fact be used for implementing other languages. Indeed, there were
successful experiments of using PyPy to implement several other languages such
as Smalltalk \cite{BolzEtAl08}, JavaScript, Scheme and Prolog.

\commentout{
As suggested by Figure~\ref{pypy-fig}, a portable interpreter for a
generic language $L$  can be
easily developed once an interpreter for $L$ has been implemented in
RPython.
}
